\ucntitlepage{%
\parbox[t]{\titlepageleftcolumnwidth}{
  \danishprojectinfo{
    QWest %title
  }{%
    5/10/20 - 21/12/20 %project period
  }{%
    Gruppe 5 % project group
  }{%
    %list of group members
    Benyad Jomhur\\ 
    Lucca Christiansen\\
    Alexandra Østermark\\
    Søren Ravn\\
  }{%
    %list of supervisors
    Lars Nysom\\
    Michael Holm Andersen\\
    Henrik Kristian Ulrik Øllgaard\\
  }{%
    \charactercount
  }{%
    \pagecount
  }{%
    \url{https://github.com/cramt/QWest/}
  }{
    \url{URL_TO_COMMIT_ON_REPO} %TODO: Update this on the 20th or 21st
  }
  \danishprojectinfocont{%
    \today % date of completion
  }%
  }
}{%department and address
  \textbf{IT-uddannelserne}\\
  Professionshøjskolen UCN\\
  \href{http://www.ucn.dk}{www.ucn.dk}
}{% the abstract
The following report describes the system development process used with the Agile development methods known as Scrum and Extreme Programming (XP). The goal of the developed system was to create a user-friendly system regarding filling out the world map based on the users' travels, for both solo and group travel, and making it possible to create and edit posts about your travels. In order to create the best possible version of an application like this one, the development process should be one that corresponds best to the group size, time frame, and type of project. With this in mind, the group analyzed 3 different development methods; The agile method, the waterfall method, and the unified process method. And with this, it was concluded that an agile would be the best approach for an application like Qwest would be the accurate approach. However, there are multiple agile methods, so again the group did an analysis of Scrum, XP, and Kanban and found a combination of Scrum and XP with a Kanban board to track progress, would likely yield the best possible result with respect to the potential of the application. The report mostly delves into the process itself, which is described through the second part of the report. The process is clearly outlined using the Scrum terminologies and XP practices, with a focus on risk management and quality assurance. The program architecture was selected to be a part of the report as well since in agile development the design of the program must be one of the first considerations before one simply starts coding.
}